\documentclass[11pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here
\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage[colorlinks=true, urlcolor=blue, linkcolor=red]{hyperref}
\usepackage{hyperref,textcomp,fontawesome5,fancyhdr, hanging}
\newsectionwidth{0pt} % Stops section indenting
\begin{document}
%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS(ES)
%----------------------------------------------------------------------------------------
\name{HUW WILLIAM CHESTON} 
%----------------------------------------------------------------------------------------
\begin{resume}
%------------------------------------------------------------==--------------
\faEnvelope \hspace{4pt} \href{mailto:hwc31@cam.ac.uk}{hwc31@cam.ac.uk}
\hfill \faGithub \hspace{4pt} \href{https://www.github.com/huwcheston}{https://www.github.com/huwcheston} \\
%------------------------------------------------------------==--------------
%	EDUCATION 
%----------------------------------------------------------------------------
\section{\centerline{EDUCATION}} 
\vspace{8pt} % Gap between title and text
\textbf{Ph.D., Music Data Science}  \hfill \emph{expected} September, 2024   \\
Centre for Music \& Science, University of Cambridge, UK \\ \\
\-\hspace{1cm} \textbf{Thesis:} Modeling Improvised Musical Interaction \emph{(preliminary title)} \\
\-\hspace{1cm} \emph{Supervisor:} Peter Harrison \& Ian Cross \\
\-\hspace{1cm} Demonstrated how tools from machine learning and data science \\ \-\hspace{1cm} can inform research on stylometry and musical improvisation

\textbf{MSt., Music}, \emph{Distinction} \hfill October, 2020\\
Linacre College, University of Oxford, UK \\ \\
\-\hspace{1cm} \textbf{Dissertation:} Making Music Alone: Time, Temporality, and Expression in Unaccompanied
\-\hspace{1cm} Jazz Improvisation \\
\-\hspace{1cm} \emph{Supervisor:} Eric Clarke \\
\-\hspace{1cm} Final mark of 85\%, \textit{graduated with the highest mark in the year}

\textbf{BA., Music}, \emph{First Class} \hfill June, 2019 \\ 
Christ Church, University of Oxford, UK \\ \\
\-\hspace{1cm} Final mark of 76\%, \textit{graduated with the highest mark in the year}
%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{\centerline{TECHNICAL SKILLS}}
\vspace{8pt} % Gap between title and text
\subsection{Programming}
\begin{itemize}
\setlength\itemsep{0pt}
    \item[--]Python \faPython \hspace{4pt}(NumPy, Pandas, Matplotlib, Seaborn, Plotly, Scikit-learn, SciPy, Statsmodels, OpenCV, Jinja, Librosa)
    \item[--]JavaScript \hspace{4pt}(JQuery, DataTable, Plotly)
    \item[--]\textsf{R} (ggplot2, lme4, tidyverse)
    \item[--] Misc.: \faGit, \LaTeX, Jupyter, Colab, PyCharm, RStudio, Docker, DataSpell, Stata, HTML, CSS
\end{itemize}
\subsection{Statistics}
\begin{itemize}
\setlength\itemsep{0pt}
    \item[--]Working with large data sets
    \item[--]Working with time-series data
    \item[--]Data wrangling and cleaning
    \item[--]Data visualisation, including interactive plots
\end{itemize}
    
%----------------------------------------------------------------------------------------
%	AWARDS AND PRIZES
%----------------------------------------------------------------------------------------
\section{\centerline{AWARDS AND PRIZES}}
\vspace{8pt} % Gap between title and text
\begin{hangparas}{.25in}{1}
\textbf{Travel Award} (\emph{£200}) \hfill  August, 2023\\
International Conference on Music Perception and Cognition \\
Travel Grant to present a paper at \emph{ICMPC17}, Tokyo, Japan

\textbf{Small Research Grant} (\emph{£500}) \hfill  August, 2023\\
Royal Musical Association \\
Travel Grant to present a paper at \emph{ICMPC17}

\textbf{Travel Grant} (\emph{£1500}) \hfill  August, 2023\\
Music \& Letters Trust \\
Travel Grant to present a paper at \emph{ICMPC17}

\textbf{Conference Paper Presentation Award} (\emph{£500}) \hfill  August, 2022\\
Cambridge Digital Humanities \\
Travel Grant to present a paper at \emph{Conference on Interdisciplinary Musicology}, Edinburgh, UK

\textbf{Project Incubation Award} (\emph{£2000}) \hfill  May, 2022\\
Cambridge Digital Humanities \\
Awarded for continual development and testing of \emph{Audio-Visual Manipulator} software for studying musical performances in experiments \href{https://www.cdh.cam.ac.uk/research/cdh-funding/newmusicsoftwareplatform/}{[Project page]}

\textbf{Vice-Chancellor's Award} (\emph{£75,000}) \hfill  September, 2021 \\
Cambridge Trust \\
Full scholarship (fees \& stipend) for Ph.D Music

\textbf{Lewis Research Scholarship in the Humanities} \hfill September, 2021 \\
Robinson College, University of Cambridge \\
Joint award with above

\textbf{Musicology Prize} (\emph{£100}) \hfill  October, 2020\\
Faculty of Music, University of Oxford \\
Awarded for highest mark in the 2020 MSt. Musicology cohort

\textbf{Louis Curran Graduate Scholarship} (\emph{£25,000}) \hfill  August, 2019\\
Linacre College, University of Oxford \\
Full scholarship (fees \& stipend) for MSt. Musicology

\textbf{Gibbs Prize in Music} (\emph{£500}) \hfill  June, 2019 \\
Faculty of Music, University of Oxford \\
Awarded for highest mark in the 2019 BA. Music cohort

\textbf{Clifford Smith Prize} (\emph{£130}) \hfill  June, 2019 \\
Christ Church, University of Oxford \\
Awarded on basis of continued academic excellence

\textbf{Academic Scholarship} (\emph{£300} x2) \hfill  September, 2018; September, 2017 \\
Christ Church, University of Oxford

\textbf{Collections Prize} (\emph{£50} x2) \hfill  September, 2018; September, 2017 \\
Christ Church, University of Oxford \\
Awarded for performance in formative examinations
\end{hangparas}
%----------------------------------------------------------------------------------------
%	PUBLICATIONS SECTION (APA)
%----------------------------------------------------------------------------------------
\section{\centerline{PUBLICATIONS}}
\vspace{8pt} % Gap between title and text
\subsection{Preprints}
\begin{hangparas}{.25in}{1}
\textbf{Cheston, H.}, Schlichting, J. S., Cross, I., \& Harrison, P. M. C. (2024). Rhythmic qualities of jazz improvisation predict performer identity and style in source-separated audio recordings \emph{PsyArXiv}. \href{https://doi.org/10.31234/osf.io/txy2f}{[https://doi.org/10.31234/osf.io/txy2f]}

\textbf{Cheston, H.}, Schlichting, J. S., Cross, I., \& Harrison, P. M. C. (2024). Cambridge jazz trio database: automated timing annotation of jazz piano trio recordings processed using audio source separation \emph{PsyArXiv}. \href{https://doi.org/10.31234/osf.io/jyqp3}{[https://doi.org/10.31234/osf.io/jyqp3]}

\textbf{Cheston, H.}, Cross, I., \& Harrison, P. (\textit{in preparation}). Trade-offs in Coordination Strategies for Networked Jazz Performances. \emph{PsyArXiv}. \href{https://doi.org/10.31234/osf.io/z8c7w}{[https://doi.org/10.31234/osf.io/z8c7w]}
\end{hangparas}

\subsection{Conference Proceedings}
\begin{hangparas}{.25in}{1}
\textbf{Cheston, H.}, Cross, I., \& Harrison, P. (2023). An automated pipeline for characterizing timing in jazz trios. Paper presented at the DMRN+18: Digital Music Research Network Workshop, Queen Mary University of London, UK. \href{https://www.qmul.ac.uk/dmrn/media/dmrn/DMRN-18-Proceedings.pdf}{[Proceedings]}

\textbf{Cheston, H.}, Cross, I., \& Harrison, P. (2023). Modelling coordination strategies in improvised musical performances by skilled jazz groups. Paper presented at the 16th International Conference of Students of Systematic Musicology (SysMus23), Sheffield University, UK. \href{https://drive.google.com/file/d/14F5Xe8qfxfWpMW6pGuIl8fcaIYbmFDtt/view}{[Proceedings]}

\textbf{Cheston, H.}, Cross, I., \& Harrison, P. (2023). Coordination strategies in networked jazz performances. Paper presented at the 17th International Conference on Music Perception and Cognition (ICMPC), Nihon University, Tokyo, Japan. \href{https://icmpc17.com/proceedings-in-zip/ICMPC17-APSCOM7-e-Proceedings.zip/}{[Proceedings]}

\textbf{Cheston, H.}, Cross, I., \& Harrison, P. (2022). The effects of variable latency timings and jitter on networked musical performances. Poster presented at the 15th International Conference of Students of Systematic Musicology (SysMus22), University of Ghent, Belgium. \href{http://hdl.handle.net/1854/LU-01GVD6WBCVPGRAHMNYR1CEXF57}{[Proceedings]}

\textbf{Cheston, H.}, Cross, I., \& Harrison, P. (2022). Measuring the effects of variable latency timings on networked jazz performances. Poster presented at the SEMPRE 50th Anniversary Conference, Senate House, University of London, UK. \href{https://drive.google.com/file/d/1P72Orm1gqSI4_gOah3Ueb9fdCpriVY_M/view}{[Proceedings]}

\textbf{Cheston, H.} (2022). "Turning the beat around": Time, temporality, and participation in the jazz solo break. Paper presented at the 13th Conference on Interdisciplinary Musicology: 'Participation', University of Edinburgh, UK. \href{http://journals.ed.ac.uk/CIM22-Proceedings}{[Proceedings]}
\end{hangparas}

\subsection{Other Publications}
\begin{hangparas}{.25in}{1}
\textbf{Cheston, H.} (2022) Conference Review: Interdisciplinary Musicology 2022: 'Participation'. Royal Musical Association. \href{https://www.rma.ac.uk/2022/06/23/conference-review-interdisciplinary-musicology-2022-participation/}{[Conference review]}
\end{hangparas}
%----------------------------------------------------------------------------------------
%	TEACHING
%----------------------------------------------------------------------------------------
\section{\centerline{TEACHING}}
\vspace{8pt} % Gap between title and text
\textbf{Guest Lecturer} \hfill Winter 2021 –\\
% Where
Faculty of Music, University of Cambridge \\
% Magnitude
Delivered guest lecture for Undergraduate level \emph{Introduction to Music Psychology} course 

\textbf{Supervisor} \hfill Spring 2022 –\\
% Where
Faculty of Music, University of Cambridge\\
% Magnitude
Delivered supervisions at Undergraduate level on: \emph{(i)} introduction to programming in Python and R; \emph{(ii)} visualising and generating data in Python and R; \emph{(iii)} writing research proposals; \emph{(iv)} analysing musical performances empirically. \\
%----------------------------------------------------------------------------------------
%	TRAINING
%----------------------------------------------------------------------------------------
\section{\centerline{TRAINING}}
\vspace{8pt} % Gap between title and text
\emph{Social Sciences Research Methods Programme}, University of Cambridge:
\begin{itemize}
\setlength\itemsep{0pt}
    \item[--] Time Series Analysis \hfill Spring, 2022
    \item[--] Further Topics in Multivariate Analysis\hfill Spring, 2022
    \item[--] Doing Multivariate Analysis\hfill Winter, 2021
    \item[--] Basic Quantitative Analysis\hfill Winter, 2021
    \item[--] Foundations in Applied Statistics\hfill Winter, 2021
\end{itemize}
%----------------------------------------------------------------------------------------
%	EXPERIENCE
%----------------------------------------------------------------------------------------
\section{\centerline{EXPERIENCE}}
\vspace{8pt} % Gap between title and text
\subsection{Non-University Teaching}
\textbf{Graduate Music Teaching Assistant} \hfill September 2020 -- June 2021 \\
Kingswood School, Bath, UK \hfill 

\textbf{Interviewer} \hfill Summer 2019 \\
Oxford Tutors, Oxford, UK \hfill 

\textbf{Private Music Tutor} \hfill Summer 2018 \\
Remote, UK \hfill 

\subsection{Music}
\textbf{Freelance Musician} \hfill September 2016 -- current \\
Professional work across the UK on Guitar, Bass Guitar. Clients include Blenheim Palace, United Grand Lodge of England, Oxford Symphony Orchestra, TRUCK Festival \hfill 

\textbf{Sound Technician} \hfill September 2016 -- current \\
Sound production, mixing, mastering for a variety of projects in both live and studio settings, clients including ATMOSPHERE Opera Festival, Oxford Playhouse \href{https://www.youtube.com/watch?v=2ccWNviTf4A&ab_channel=HuwCheston}{[Showreel link]}\hfill 

\textbf{Administrator}, WallpaperJazz \href{https://wallpaperjazz.wordpress.com/}{[Website link]} \hfill June 2016 -- current \\
Online blog hosting transcriptions  of jazz improvisations, currently averaging 1000+ worldwide views monthly across 75 countries.
%----------------------------------------------------------------------------------------
%	REFERENCES
%----------------------------------------------------------------------------------------
\section{\centerline{REFERENCES}} \
\vspace{8pt}
\centerline{\textbf{Available on request}}

\end{resume} 
\end{document}